\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-09-11 paper.tex
add pseudo code

\section{MCMC-based Informed Sampling}
In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~1).
This sample is used to produces a 
sample~$x_0 \in \partial\Cinf$ 
%sample~$x_\text{boundary} \in \partial\Cinf$ 
which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad})by applying Newton-Raphson method~\cite{RT06} (line~2).
Finally,~$x_0$ 
%use~$x_\text{boundary}$ 
is used (lines~3-5)
to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}). Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
For a visualization of the approach, see Fig.~\ref{fig:alg}.

@@

@@

>>>>

\section{MCMC-based Informed Sampling}

In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~1).
This sample is used to produces a 
sample~$x_0 \in \partial\Cinf$ 
%sample~$x_\text{boundary} \in \partial\Cinf$ 
which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad})by applying Newton-Raphson method~\cite{RT06} (line~2).
Finally,~$x_0$ 
%use~$x_\text{boundary}$ 
is used (lines~3-5)
to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}). 
%Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
For a visualization of the approach, see Fig.~\ref{fig:alg}.

@@

\dy{Basically we follows a MCMC framework for informed sampling, which takes the advantage of a balanced exploration and exploitation.
Under the MCMC framework, we use both Metropolis-Hastings and Hit-And-Run to generate samples.
}

@@

(a) we use Metropolis-Hasting

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
		\STATE $ \alpha = \frac{ P( x'_{i} ) }{ P( x_{i} ) } $ 
		\IF{ $ random() \leq \alpha $ \AND \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
		  \STATE $ x_{i+1} \leftarrow x'_{i+1} $ 
		\ELSE
		  \STATE $ x_{i+1} \leftarrow x_{i} $
		\ENDIF 
	\end{algorithmic}
	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
	\label{alg:mh_mcmc}	
\end{algorithm}

\subsection{Sampling using Hit-And-Run Sampler}

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE Sample random direction in $ d_i $
		\STATE Find the line set $ L = \{  x \mid x = x_i + \lambda d_i \} $
		\STATE $ \lambda^{+} \leftarrow \sup L $, $ \lambda^{-} \leftarrow \inf L $
		\STATE $ \lambda'_{i} \leftarrow ( \lambda^{-} , \lambda^{+} ) $
		\STATE $ x'_{i+1} = x_{i} + \lambda'_{i} d_i $
		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $ }
		  \STATE $ x_{i+1} = x'_{i+1} $
 		\ELSE
		  \IF{ $ \lambda'_{i} > 0 $ }
			  \STATE $ \lambda^{+} \leftarrow \lambda'_{i} $
		  \ELSE
			  \STATE $ \lambda^{-} \leftarrow \lambda'_{i} $
		  \ENDIF 
		  \STATE go back to line 4
		\ENDIF 	
	\end{algorithmic}
	\caption{Hit-And-Run MCMC $(x_{i}, c_{\text{best}})$}
	\label{alg:hit_and_run_mcmc}	
\end{algorithm}
